Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-06 ms.tex
updated figures

\begin{document} 
\shorttitle{MachLensFinder}
\shortauthors{Avestruz, Li, Lightman}
\submitted{The Astrophysical Journal} 
\slugcomment{The Astrophysical Journal, submitted}

\title{MachLensFinder - I: An automated Strong Lensing
  Identification Pipeline}

@@

%-------------------------------------------------%
\begin{abstract} 
Gravitational lensing offers a direct probe of the underlying mass
distribution of lensing systems, a window to the high redshift
universe, and a geometric probe of cosmological models.  The advent of
large scale surveys such as the Large Synoptic Sky Telescope and
Euclid has prompted a need for automatic and efficient identification
of strong lensing systems.  We present {\em MachLensFinder}, a
strong lensing identification pipeline that will be publicly released
as open source software.  In this first application, we employ a fast
feature extraction method, Histogram of Oriented Gradients (HOG), to
capture edge patterns that are characteristic of strong gravitational
arcs in galaxy-galaxy lensing.  We use logistic regression to train a
supervised classifier model on the HOG of \change{HST- and LSST}-like
images.  Our best performing models reach a completeness rate of
\change{XX\%} and purity rate of \change{XX\%} for an HST-like sample.
However, for one orbit of LSST, our model cannot distinguish between
strong lensing systems and non-strong lensing systems.  In absence of
the brightest cluster galaxy in LSST-like data, our trained model
reaches a completeness of \change{XX\%} and purity of \change{XX\%}.
Our results show one the most efficient and effective methods for
automated strong lensing identification in space-based surveys.  The
results also emphasize the need for further development and testing of
additional tools to maximize use of ground-based surveys.
\end{abstract}
%-------------------------------------------------%

@@

% Gravitational lensing as a geometric (?) test of cosmology.  Also
% probes underlying matter distribution in galaxy clusters, sensitive
% to things like recent accretion and environment.
Gravitational lensing occurs when intermediate fluctuations in the
matter density field deflect light from background sources
\citep[see][for a review]{kneibandnatarajan_11}.  Strong gravitational
lensing can manifest as visible giant arcs magnifying high redshift
galaxies \citep{lyndsandpetrosian_86,gladders_etal03}, multiply imaged
quasars \citep{walsh_etal79}, and arclets.  Lensing signatures probe
the underlying dark matter distribution of the lens
\citep{warrenanddye_03}, high redshift galaxy formation
\citep{allam_etal07}, and provide a geometric test of cosmology via
comparison of predicted arc abundances and observed abundances
\citep{kochanek_96,chae_03,linder_04}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:mockimages}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1_color.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_unlensed_imgs_1_color.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1.pdf}
\caption{Top row: Example mock HST images, with $n_\text{pix}\times
  n_\text{pix}=300\times300$.  The left corresponds to a strong
  gravitational lensing system with a visibly obvious giant arc.  The
  right corresponds to a non-lensing system.  Middle row: Example mock
  LSST images for a single epoch, with $n_\text{pix}\times
  n_\text{pix}=45\times45$.  The resolution and noise of a ground
  based telescope is noticeably worse.  The left and right images
  correspond to the same systems as the top row.  However, visual
  identification of giant arcs in the LSST images is very difficult.
  Bottom row: Example mock LSST images for stacked data over the 10
  year run.  Here, the arc is more visible, but not as well resolved
  as in the HST case.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

To perform our analysis, we have used a variety of tools from {\em
  Scikit-learn} \citep{pedregosa_etal12}.  We outline the
identification pipeline in Figure~\ref{fig:pipeline}.  The first step
of our pipeline consists of a feature extraction stage, where our
feature vector is a {\em histogram of oriented gradients}
\citep{dalalandtriggs_05}.  We describe the method in
Section~\ref{sec:hog}.  We then use a machine learning algorithm to
train a classifier model on a subset of our images.  We have explored
both {\em Logistic Regression} (LR) and {\em Support Vector Machine}
(SVM) machine learning algorithms.  We test our trained model on an
independent subset of the images to assess the model performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
%\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
%\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
\caption{Top row: Visualized HOG feature vectors of the sample lensed
  HST-like image from Figure~\ref{fig:mockimages}.  Left: The
  corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
  pixels per cell, and (1, 1) cells per block.  Right: The HOG
  visualization of the same mock image with N$_\text{orient}=9$, (16,
  16) pixels per cell, and (1, 1) cells per block.  The brightest
  lines align with prominent edges.  Note, while fewer pixels per cell
  will better resolve the arc feature, the ``edge'' corresponding to
  the arc is less prominent.  Bottom row: Visualized HOG feature
  vectors for the LSST-like single epoch and stacked images with the
  best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
  pixels per cell, and (3, 3) cells per block.  The single epoch image
  (left) does not have significant enough edge features to emerge in
  the HOG, but the stacked image (right) does.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Note, we also include the size of the extracted features, e.g. the
length of the HOG feature vector.  A longer feature vector will
increase the amount of time required to train the model.
Additionally, for fixed memory restrictions, there is a tradeoff
between the length of the feature vector and the size of the training
set.  The logistic regression coefficient will also increase the
training time, \todo{since larger coefficients correspond to a more
  singular matrix}.  We discuss the score dependence on logistic
regression coefficient in Section\ref{sec:unregularizedfit}.

%-------------------------------------------------%
\subsection{Receiver Operatic Characteristic}
%-------------------------------------------------%

In this section, we discuss the Receiver Operating Characteristic
(ROC) curve, which shows the true positive rate as a function of false
positive rate for a given model and test set.  The true positive rate
is defined as the number of true positives divided by the total number
of positives (completeness of the positive identifications).  The
false positive rate is defined as the number of false positives
divided by the total number of negatives (impurity of the
identifications).  The ROC curve illustrates the performance of our
trained model as we vary the discrimination threshold.

The classifier model assigns a score to each test image, which is a
probability that the image is a strong lensing system.  To construct
the ROC curve, the test images are ranked by probability and the
discrimination threshold varied.

For very high discrimination threshold, we have maximal purity, but a
low completeness (bottom left region of the ROC).  FOr a very low
discrimination threshold, we have maximal completeness, but minimal
purity (top right region of the ROC).  The ideal model would have a
data point on the ROC curve that sits on the top left corner,
i.e. $(x, y) = (0, 1)$.

In the context of strong lensing systems, we wish to maximize the true
positive rate so we have a representative count of the fraction of
strong lensing systems in an observed volume of the universe.  We also
want to minimize the false positive rate.  Positively identified
strong lensing systems will require expensive spectroscopic follow-up
for validation.  The steepness of the ROC curve indicates how well the
model will optimize the two, and we can characterize the steepness by
the area under the curve (AUC).  A perfect model would have an AUC of
1, with data points along $(x=0, 0\leq y\leq1)$, and $(0\leq x\leq 1,
y=1)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:ROCHST}
\begin{center}
\includegraphics[width=\columnwidth]{figures/ROC_HST_HOG.png}
\caption{Red, green, blue: ROC curves for a models trained on the
  HST-like data with the Logistic Regression algorithm.  The magenta
  solid (dotted) curve show the ROC curve for the LSST-like data with
  (without) the BCG.  The corresponding parameters are labeled: N for
  number of orientations, ppc for pixels-per-cell, cpb for
  cells-per-block, and C for best regularization parameter.  The AUC
  for each model is also labeled in the legend, where an AUC close to
  1 is a near-ideal model, and an AUC close to 0.5 is a model that
  performs as well as a coin-flip.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:ROCLSST}
\begin{center}
\includegraphics[width=\columnwidth]{figures/ROC_LSST_HOG.png}
\caption{Red, green, blue: ROC curves for a models trained on the
  HST-like data with the Logistic Regression algorithm.  The magenta
  solid (dotted) curve show the ROC curve for the LSST-like data with
  (without) the BCG.  The corresponding parameters are labeled: N for
  number of orientations, ppc for pixels-per-cell, cpb for
  cells-per-block, and C for best regularization parameter.  The AUC
  for each model is also labeled in the legend, where an AUC close to
  1 is a near-ideal model, and an AUC close to 0.5 is a model that
  performs as well as a coin-flip.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Effects of Regularization on Model Performance}\label{sec:regularizedfit}
%-------------------------------------------------%

% Logistic regression and regularization
As described in Section~\ref{sec:logreg}, logistic regression trains a
model with complexity determined by the regularization parameter,
$C_\text{LogReg}$.  Increasing model complexity (larger
$C_\text{LogReg}$), will better describe features in the training
set[wc?].  However, an overly complex model will overfit the training
set at the expense of its performance on any independent test set.
The regularization parameter ultimately defines the model performance,
and we must perform a parameter search to identify the optimal value
for $C_\text{LogReg}$.

@@

% Training behavior with C
For either characterization of the model, the model performance on the
training set increases and asymptotes with $C_\text{LogReg}$.  With
increasing model complexity, the model better fits the data set it has
been trained on.  [wc???] This is analogous to fitting a seventh order
polynomial to seven data points, where the fitting function will go
through every point but will not likely predict additional points.

% Test behavior with C
We use the model performance on a test set to determine the best value
for $C_\text{LogReg}$ that will not overfit the training data.  With
increasing model complexity, we are able to better able to capture
features that are generally characteristic of strong lensing systems
with arcs.  However, past a certain $C_\text{LogReg}$, the model
performance on the test set decreases, as it has overfit the training
set.

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:regularization}
\begin{center}
\includegraphics[width=\columnwidth]{figures/regularized_accuracy.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/regularized_AUC.pdf}
\caption{Left: Accuracy of the model with varying regularization.
  Each color corresponds to a model trained for features extracted
  with a different set of HOG parameters.  The dotted (solid) lines
  show the performance of the model on the training (test) set.
  Right: AUC of the model with varying regularization.  Linestyles and
  colors are similar to those in the left panel.  AUC is a better
  characterization of model performance, since the accuracy is
  determined for fixed classification threshold [wc?], but peak model
  performance can occur at a different classification threshold.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Image classification performance}\label{sec:performance}
%-------------------------------------------------%
**Redshift makes sense, but only because of the redshift distribution.
--> Zahid+15 quiescent.... this is where redshifts are from.

>>>>

\begin{document} 
\shorttitle{Automated Lensing Learner}
\shortauthors{Avestruz, Li, Lightman}
\submitted{The Astrophysical Journal} 
\slugcomment{The Astrophysical Journal, submitted}

\title{Automated Lensing Learner - I: An automated Strong Lensing
  Identification Pipeline}

@@

%-------------------------------------------------%
\begin{abstract} 
Gravitational lensing offers a direct probe of the underlying mass
distribution of lensing systems, a window to the high redshift
universe, and a geometric probe of cosmological models.  The advent of
large scale surveys such as the Large Synoptic Sky Telescope and
Euclid has prompted a need for automatic and efficient identification
of strong lensing systems.  We present {\em (ALL) Automated Lensing
  Learner}, a strong lensing identification pipeline that will be
publicly released as open source software.  In this first application,
we employ a fast feature extraction method, Histogram of Oriented
Gradients (HOG), to capture edge patterns that are characteristic of
strong gravitational arcs in galaxy-galaxy lensing.  We use logistic
regression to train a supervised classifier model on the HOG of HST-
and LSST-like images.  We use an area under the curve (AUC) of a
Receiver Operating Characteristic curve to assess model performance;
$AUC=1.0$ is an ideal trained classifier, and $AUC=0.5$ does not
provide any classification information.  Our best performing models
exhibit an AUC of \change{XX} for an HST-like sample.  However, for
one orbit of LSST, our model only reaches an AUC of \change{XX}.  In
absence of the lens galaxy in one orbit of LSST-like data, the AUC
improves to \change{XX}.  For 10-year mock LSST observations, the
respective AUC with and without the lens galaxy improves to
\change{XX} and \change{XX}.  Our results show an efficient and
effective methods for automated strong lensing identification.  The
results also emphasize the need for further development and testing of
additional tools to maximize use of ground-based surveys.
\end{abstract}
%-------------------------------------------------%

@@

% Gravitational lensing as a geometric (?) test of cosmology.  Also
% probes underlying matter distribution in galaxy clusters, sensitive
% to things like recent accretion and environment.
Gravitational lensing occurs when intermediate fluctuations in the
matter density field deflect light from background sources
\citep[see][for a review]{kneibandnatarajan_11}.  Strong gravitational
lensing can manifest as visible giant arcs magnifying high redshift
galaxies \citep{lyndsandpetrosian_86,gladders_etal03}, multiply imaged
quasars \citep{walsh_etal79}, and arclets.  Lensing signatures probe
the underlying dark matter distribution of the lens
\citep{warrenanddye_03}, high redshift galaxy formation
\citep{allam_etal07}, and provide a geometric test of cosmology via
comparison of predicted arc abundances and observed abundances
\citep{kochanek_96,chae_03,linder_04} and time-delay signals from
multiply imaged quasars ???\citep{}.

% Application of constraining mass profiles - large numbers needed.
The application of strong gravitational lensing to constrain the mass
distribution of \todo{early-type galaxies (ETGs)} necessitates large
samples of galaxy-galaxy lensing systems.  The strong lensing
signature... EDITING HERE These systems exhibit a background source
galaxy that the ETG deflects into a partial of full arc shaped
Einstein ring.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:mockimages}
\begin{center}
\includegraphics[width=2\columnwidth]{figures/tiles/compilations/telescope_compilation.pdf}
\caption{Left to right show example mock HST, LSST 10 year, and LSST 1
  year images.  The top row corresponds to a lensing system with a
  very visible arc signature, and the bottom row to a lensing system
  that is less obvious.  Example mock HST images have
  $n_\text{pix}\times n_\text{pix}=300\times300$.  Example mock LSST
  images have $n_\text{pix}\times n_\text{pix}=45\times45$.  The
  resolution and noise of a ground based telescope is noticeably
  worse. Visual identification of giant arcs in the LSST images in the
  bottom row is very difficult.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

To perform our analysis, we have used a variety of tools from {\em
  Scikit-learn} \citep{pedregosa_etal12}.  We outline the
identification pipeline in Figure~\ref{fig:pipeline}.  The first step
of our pipeline consists of a feature extraction stage, where our
feature vector is a {\em histogram of oriented gradients}
\citep{dalalandtriggs_05}.  We describe the method in
Section~\ref{sec:hog}.  We then use a machine learning algorithm to
train a classifier model on a subset of our images.  We have explored
both {\em Logistic Regression} (LogReg) and {\em Support Vector Machine}
(SVM) machine learning algorithms.  We test our trained model on an
independent subset of the images to assess the model performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:mockimages}
\begin{center}
\includegraphics[width=2\columnwidth]{figures/tiles/compilations/hog_telescope_compilation.pdf}
\caption{Left to right show example image transforms of mock images
  from Figure~\ref{fig:mockimages} with a visualized histogram of
  oriented gradients.  The image transform picks up edge features,
  with arc features showing up as edges across radial orientations.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%% \begin{figure*}[t]\label{fig:hogvisual}
%% \begin{center}
%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
%% \includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
%% %\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
%% \includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
%% %\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
%% \caption{Top row: Visualized HOG feature vectors of the sample lensed
%%   HST-like image from Figure~\ref{fig:mockimages}.  Left: The
%%   corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
%%   pixels per cell, and (1, 1) cells per block.  Right: The HOG
%%   visualization of the same mock image with N$_\text{orient}=9$, (16,
%%   16) pixels per cell, and (1, 1) cells per block.  The brightest
%%   lines align with prominent edges.  Note, while fewer pixels per cell
%%   will better resolve the arc feature, the ``edge'' corresponding to
%%   the arc is less prominent.  Bottom row: Visualized HOG feature
%%   vectors for the LSST-like single epoch and stacked images with the
%%   best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
%%   pixels per cell, and (3, 3) cells per block.  The single epoch image
%%   (left) does not have significant enough edge features to emerge in
%%   the HOG, but the stacked image (right) does.}
%% \end{center}
%% \end{figure*}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Note, we also include the size of the extracted features, e.g. the
length of the HOG feature vector.  A longer feature vector will
increase the amount of time required to train the model.
Additionally, for fixed memory restrictions, there is a tradeoff
between the length of the feature vector and the size of the training
set.  The logistic regression coefficient will also increase the
training time, \todo{since larger coefficients correspond to a more
  singular matrix}.  We discuss the score dependence on logistic
regression coefficient in Section\ref{sec:regularization}.

%-------------------------------------------------%
\subsection{Receiver Operating Characteristic}
%-------------------------------------------------%

In this section, we discuss the Receiver Operating Characteristic
(ROC) curve, which shows the true positive rate (tpr) as a function of
false positive rate (fpr) for a given model and test set.  The true
positive rate is defined as the number of true positives divided by
the total number of positives (completeness of the positive
identifications).  The false positive rate is defined as the number of
false positives divided by the total number of negatives (impurity of
the identifications).  The ROC curve illustrates the performance of
our trained model as we vary the discrimination threshold.

The classifier model assigns a score to each test image, which is a
probability that the image is a strong lensing system.  To construct
the ROC curve, we rank the test images by probability, and calculate
the tpr and fpr for decreasing discrimination threshold.

For very high discrimination threshold, we have maximal purity, but a
low completeness (bottom left region of the ROC).  For a very low
discrimination threshold, we have maximal completeness, but minimal
purity (top right region of the ROC).  The ideal model would have an
ROC curve with data points that go from $(x, y) = (0, 0)$ to $(x, y) =
(0, 1)$ to $(x, y) = (1, 1)$.

In the context of strong lensing systems, we wish to maximize the true
positive rate so we have a representative count of the fraction of
strong lensing systems in an observed volume of the universe.  We also
want to minimize the false positive rate.  Positively identified
strong lensing systems will require expensive spectroscopic follow-up
for validation.  The steepness of the ROC curve indicates how well the
model will optimize the two, and we can characterize the steepness by
the area under the curve (AUC).  The ideal model would have an AUC of
1.  We show the ROC curves of our best performing models in each
dataset.

@@

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
%% \begin{figure}[t]\label{fig:ROCHST}
%% \begin{center}
%% \includegraphics[width=\columnwidth]{figures/ROC_HST_HOG.png}
%% \caption{Red, green, blue: ROC curves for a models trained on the
%%   HST-like data with the Logistic Regression algorithm.  The magenta
%%   solid (dotted) curve show the ROC curve for the LSST-like data with
%%   (without) the BCG.  The corresponding parameters are labeled: N for
%%   number of orientations, ppc for pixels-per-cell, cpb for
%%   cells-per-block, and C for best regularization parameter.  The AUC
%%   for each model is also labeled in the legend, where an AUC close to
%%   1 is a near-ideal model, and an AUC close to 0.5 is a model that
%%   performs as well as a coin-flip.}
%% \end{center}
%% \end{figure}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:ROCcompilation}
\begin{center}
\includegraphics[width=\columnwidth]{figures/metrics/ROC/ROC_compilation.pdf}
\caption{Red, blue, green: ROC curves for models trained on our whole
  10,000 training set and tested on our holdout set of 1,000.  These
  respectively correspond to the HST, LSST 1 year, and LSST 10 year
  data.  The solid lines are for data that include the lensing central
  galaxy, and the dashed lines for the data where there is no lensing
  galaxy, mimicking an ideal removal of the lens.  Model performance
  can be summarized by the area under the curve (AUC), labeled in the
  legend. $AUC=1$ is a perfect model, and $AUC=0.5$ is a useless
  model.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Effects of Regularization on Model Performance}\label{sec:regularization}
%-------------------------------------------------%

% Logistic regression and regularization
As described in Section~\ref{sec:logreg}, LogReg trains a model with
complexity determined by the regularization parameter coefficient,
$C_\text{LogReg}$.  Increasing model complexity (larger
$C_\text{LogReg}$), will better describe features in the training
set[wc?].  However, an overly complex model will overfit the training
set at the expense of its performance on any independent test set.
The regularization parameter ultimately defines the model performance,
and we must perform a parameter search to identify the optimal value
for $C_\text{LogReg}$.

@@

% Training behavior with C
For either characterization of the model, the model performance on the
training set increases and asymptotes with $C_\text{LogReg}$.  With
increasing model complexity, the model better fits the data set it has
been trained on.  This is analogous to fitting a seventh order
polynomial to seven data points, where the fitting function will go
through every point but will not likely predict additional points.

% Test behavior with C
We use the model performance on a test set to determine the best value
for $C_\text{LogReg}$ that will not overfit the training data.  With
increasing model complexity, we are able to better able to capture
features that are generally characteristic of strong lensing systems
with arcs.  However, past a certain $C_\text{LogReg}$, the model
performance on the test set decreases or asymptotes, as it has overfit
the training set.

% Train time with Creg
Lower Creg, more regularized, smaller volume to search for the
solution (best fit coefficients), so faster on average.  But, still
has some randomness associated with the path it takes to convergence
(not purely monotonic).

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:regularization}
\begin{center}
\includegraphics[width=.66\columnwidth]{figures/Creg/HST.pdf}
\includegraphics[width=.66\columnwidth]{figures/Creg/LSST1.pdf}
\includegraphics[width=.66\columnwidth]{figures/Creg/LSST10.pdf}
\caption{AUC of the model with varying LR regularization coefficient
  parameter, $C_{reg}$, used when training the model classifier.  We
  use a subset of the the 10,000 training images to search over the LR
  $C_{reg}$ parameter, training on 8,000 and testing on 1,000.  Each
  panel corresponds to a different mock observation.  From left to
  right: HST, LSST for one year, and LSST for 10 years.  The xsolid
  blue lines correspond to the AUC of the training set, and the dotted
  blue lines to the AUC of the test set.  To avoid overfitting, we
  choose the smallest parameter for which the AUC of the test set is
  maximal: 5000, 10, and 5000, respectively.  In thin red solid lines,
  we show the train time of the model, which roughly increases in a
  log-log scaling with logistic regression coefficient parameter.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Effects of Dataset Size on Model Performance}\label{sec:datasize}
%-------------------------------------------------% 
%-------------------------------------------------% 
\subsubsection{Effects of Training Set Size}
%-------------------------------------------------% 
In this section, we show the effects of training set size on model
performance.  Figure~\ref{fig:trainsize} shows the AUC and the train
time depend on the log of the size of the training set.  In solid blue
lines, we see that the AUC improves almost linearly with the log of
the training size set.  In dotted red, we see that the train time
roughly scales logarithmically with the log of the train size, with an
exception of the data point corresponding to train size of 2000.

Each model was trained with the same HOG parameterization from the
grid search and the optimal regularization parameter for that subset
train data.  The train time of a given model generally increases for
increasing regularization parameter.  For the subset of train size
2000, the optimal regularization parameter happened to be
$C_{LR}=100$, whereas it was $C_{LR}=500$ for the subset of trainsize
1000, and $C_{LR}=1000$ for the subset of trainsize 4000.

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:trainsize}
\begin{center}
\includegraphics[width=\columnwidth]{figures/trainsize/LSST10.pdf}
\caption{Solid blue line: AUC for models with varying size of the
  training set for LSST10.  Dotted red line: Train time for that
  model.  The improvement of AUC scales linearly with the log of the
  training set size, but train time roughly scales logarithmically.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------% 
\subsubsection{Effects of Rotation on AUC}
%-------------------------------------------------% 
To augment our training set, we rotated each image in the set by
multiples of $90^o$.  The augmentation (factor of four) naturally
optimizes the use of available training data, since our feature
extraction method of HOG is not rotationally invariant.

We also tested the effects of testing our model on all four rotations
of the test set.  In Figure~\ref{fig:rotation_test}, we show the AUC
for different orientations of the datasets.  The x-axis corresponds to
each of our three datasets, \todo{with and without the lens galaxy}.
The y-axis shows the AUC.  The filled blue circles correspond to the
four AUCs calculated from test scores assigned to images at one
rotation.  The filled red stars correspond to the AUC calculated from
the average of all four test scores, which are systematically higher
than any one rotation.  The average score across all rotations for
each image is likely to be less noisy for the whole test sample,
giving an improved AUC.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:rotation_test}
\begin{center}
\includegraphics[width=\columnwidth]{figures/rotated_aucs/rotated_aucs.pdf}
\caption{The AUCs of models trained on the full 10,000 and tested on
  the holdout 1,000.  Blue circles: AUC calculated from scores of
  images at a given rotation (e.g. 0, 90, 180, and 270 degrees).  Red
  stars: AUC calculated from the average score of all rotations of
  each image.  The average score produces an improved AUC in all data
  sets.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Image classification performance}\label{sec:performance}
%-------------------------------------------------%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:ROCsamplesLSST10}
\begin{center}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tp.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/fp.pdf}\\\vspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/bp.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/bn.pdf}\\\vspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/fn.pdf}\hspace{5pt}
\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tn.pdf}\\
\caption{LSST mock images over 10 years. Left two columns: Lens
  containing images, annotated with the image score assigned by our
  trained classifier.  Right two columns: Non-lens containing images,
  annotated with the image score.  The top two rows show
  characteristic images that will be accepted with a high threshold
  for classification, contributing to the bottom left of the ROC
  curve.  The middle two rows show characteristic images that will be
  accepted with a moderate threshold, contributing to the knee of the
  ROC curve.  The bottom two rows show characteristic images that will
  only be accepted with an extremely lenient threshold, contributing
  to the top right area of the ROC curve.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

**Redshift makes sense, but only because of the redshift distribution.
--> Zahid+15 quiescent.... this is where redshifts are from.
